Verifying Demonstrations

### 2017-08-18 properties.tex
Moves some stuff back from design to properties

\mode*
\section{Verification and privacy}
\label{VerificationAndPrivacy}

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.
To have any verifiability, we need the storage to be immutable --- i.e.\ it 
prevents malicious changes.

\begin{frame}<presentation>
  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly (e.g.\ anonymous blackboard).
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\Cref{CountOnce} is required to prevent Sybil attacks.
I.e.\ that one individual can provide two proofs of participation and thus be 
counted twice, this situation should be detectable.

@@

\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.
\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{verify the data spatially}.
Finally, there might be the case that there is also a counter protest at the 
same time, these would have the same spatial and temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated (\cref{DesignatedEvent}).

\begin{frame}<presentation>
  \begin{idea}[Created after start, before end]
    \begin{itemize}
      \item This implies a partially ordered set.
      \item Can be provided by blockchains.
      \item \dots or transactional 
        posets~\cite{BlockchainFreeCryptocurrencies}.
    \end{itemize}
  \end{idea}

@@

  \begin{idea}[At location]
    \begin{itemize}
      \item Use \iac{LP}.
      \item Witnessed (signed) by other participants.
    \end{itemize}
  \end{idea}
\end{frame}

If the storage is public, then anyone can download all the proofs, verify them 
and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

\begin{frame}<presentation>
  \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}

@@

  \begin{idea}[P\ref{VotePrivacy} Vote privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.
      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}<presentation>
  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness (deniability)]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.

>>>>

\mode*
\section{The idea}
\label{TheIdea}

@@

@@

\subsubsection{Temporal eligibility}

\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}.
For generality, we will use the terminology of 
\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
structure \iac{tposet}.

\begin{frame}<presentation>
\begin{idea}[Temporal eligibility]
  \begin{itemize}
    \item There is a mechanism that provides the properties of a poset: a 
      blockchain.

    \item There are also other structures, e.g.\ a directed 
      graph~\cite{BlockchainFreeCryptocurrencies}.
  \end{itemize}
\end{idea}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
Then we know that they cannot have been created after the event.

\begin{frame}<presentation>
  \begin{idea}[Created before end]
    \begin{itemize}
      \item Submit the proof to storage.
      \item The proof must've been created before it was included (duh!).
    \end{itemize}
  \end{idea}
\end{frame}

For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
This means that they cannot create a proof and keep it for a future protest.

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval.

\begin{frame}<presentation>
  \begin{idea}[Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the proof.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{question}
  How hard is it to reuse old proofs?
  Forge all signatures due to changed values?
\end{question}

\subsubsection{Spatial eligibility}

\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{verify the data spatially}.

If we include \iac{LP}, this will tie the proof to the physical location and, 
thus, solve \cref{SpatiallyRelated}.
The \ac{LP} is \enquote{witnessed} (signed) by other participants.
The \ac{LP} contains coarse coordinates of the location, which must be within 
the protest area to be valid.
This allows Bob the protester to move within the protest area to collect 
witnesses (signatures).
It also provides privacy since the location cannot be used to deanonymize Bob's 
proof --- e.g.\ to correlate the location in his proof with captured 
surveillance footage.

\begin{frame}<presentation>
  \begin{idea}[Spatial eligibility]
    \begin{itemize}
      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
        participants.
      \item We have a coarse location, just within protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{question}
  How can we do \acp{LP} with 1000s of witnesses each?
  Can we do some preprocessing?
  Ad-hoc networks, broadcast \acp{LP}?
\end{question}
\begin{question}
  Why should anyone trust these witnesses?
  What are the assumptions?
  Signed over a short period of time?\footnote{%
    In a sense, if they collude they have shown support for the cause.
    As long as they are not Sybil it should be fine?
  }
\end{question}
\begin{question}
  Trusted party for the group signatures?
\end{question}
\begin{question}
  Must tie credentials to something unique: phone, phone subscription?
  Cannot register twice, government control?
\end{question}

\begin{question}
  What if Alice acts as a witness for Eve's agents?
  Can that violate her privacy?
\end{question}
\begin{question}
  What if Eve's agents act as witnesses?
  Can they track their signatures to track users?
  Can Alice detect if this happens?
\end{question}

\subsubsection{Linkability and designated protest}

\Cref{CountOnce} is required to prevent Sybil attacks.
I.e.\ that one individual can provide two proofs of participation and thus be 
counted twice, this situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
This can be done by including a signature made by a verified key.

There might be the case that there is also a counter protest at the same time, 
these would have the same spatial and temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated (\cref{DesignatedEvent}).
This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
its \enquote{manifesto}.

@@

\subsubsection{Individual and universal verifiability}

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.
Similarly for universal verifiability.
If the storage is public, then anyone can download all the proofs, verify their 
eligibility and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
To have any verifiability, we need the storage to be immutable --- i.e.\ it 
prevents malicious changes.

\begin{frame}<presentation>
  \begin{idea}[Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}

@@

  \begin{idea}[Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}

@@

  \begin{idea}[Vote privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.
      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}<presentation>
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.
